timesliced_random_cell_selection

### 2018-11-19 src/timesliced_random_cell_selection.Rmd
obs_by_cell inc depth for background

```{r pre-install & load packages, include=FALSE}
install.packages("pacman")
library(pacman)
p_load(raster, dplyr, data.table, sp, adehabitatHR, rgdal, rworldmap, ncdf4, marmap)
```

@@

```{r observation by cell - total}
library(plyr) #to use the count function
obs_by_cell <- count(data_aea, "cell_id")
obs_by_cell
write.csv(obs_by_cell, file = "../output/bio/no_observations_cell.csv")
```

```{r}
obs_cell_yymm <- count(data_aea, c("cell_id", "year", "month"))
obs_cell_yymm
write.csv(obs_cell_yymm, file = "../output/bio/no_observations_cell_yymm.csv")
```
Now attach these values to data_aea....

total obs for the whole time period
```{r}
data_aea <- merge(data_aea, obs_by_cell, by="cell_id")
head(data_aea)
```
rename freq column to something meaningful

```{r}
names(data_aea)[names(data_aea)=="freq"] <- "total_cell_obs"
head(data_aea)
```

time-sliced
```{r}
data_aea <- merge(data_aea, obs_cell_yymm, by.x=c("cell_id", "year", "month"), by.y=c("cell_id", "year", "month"))
names(data_aea)[names(data_aea)=="freq"] <- "yymm_cell_obs"
head(data_aea)
```

write to .csv
```{r}
write.csv(data_aea,"../output/bio/data_aea_cell_amo_nao_bins_env_depth_cellobno.csv", row.names = FALSE)
```
`

>>>>

```{r pre-install & load packages, include=FALSE}
install.packages("pacman")
library(pacman)
p_load(raster, dplyr, data.table, sp, adehabitatHR, rgdal, rworldmap, ncdf4, marmap, plyr)
```

@@

```{r observation by cell - total}
obs_by_cell_back <- count(background_all, "cell_id")
write.csv(obs_by_cell_back, file = "../output/bio/back_no_observations_cell.csv")
head(obs_by_cell_back)
```

```{r}
obs_cell_yymm_back <- count(background_all, c("cell_id", "year", "month"))
write.csv(obs_cell_yymm_back, file = "../output/bio/back_no_observations_cell_yymm.csv")
head(obs_cell_yymm_back)
```

```{r}
obs_cell_yymm_depth_back <- count(background_all, c("cell_id", "year", "month", "depthlayerno"))
write.csv(obs_cell_yymm_depth_back, file = "../output/bio/back_no_observations_cell_yymm_depth.csv")
head(obs_cell_yymm_depth_back)
```

Now attach these values to data_aea....

total obs for the whole time period
```{r}
background_all <- merge(background_all, obs_by_cell_back, by="cell_id")
head(background_all)
```

rename freq column to something meaningful
```{r}
names(background_all)[names(background_all)=="freq"] <- "total_cell_obs"
head(background_all)
```

```{r}
randcheckcell <- background_all[sample(nrow(background_all), 10), ]
randcheckcell
```
all good

time-sliced
```{r}
background_all <- merge(background_all, obs_cell_yymm_back, by.x=c("cell_id", "year", "month"), by.y=c("cell_id", "year", "month"))
background_all <- merge(background_all, obs_cell_yymm_depth_back, by.x=c("cell_id", "year", "month", "depthlayerno"), by.y=c("cell_id", "year", "month", "depthlayerno"))
names(background_all)[names(background_all)=="freq"] <- "yymm_cell_obs"
names(background_all)[names(background_all)=="freq"] <- "yymmdepth_cell_obs"
write.csv(background_all,"../output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname_bath_cellobs.csv", row.names = FALSE)
head(background_all)
```

and just check some random rows...

```{r}
randcheckyymm <- background_all[sample(nrow(background_all), 10), ]
randcheckyymm
```
